\documentclass[a4paper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{hyperref}

\pagestyle{empty}

\begin{document}

% Title
\begin{center}
    \textbf{\Large Lucca Bonanno de Almeida Cazarine}
\end{center}

% Contact information
\begin{center}
 Rua Doutor Vila Nova, 327 | São Paulo - SP | Phone: +55 (11)99295-2087 | Email: cazarinelucca@gmail.com \\\
 GitHub: \href{https://github.com/LuccaCazarine}{GitHub Profile} \\
 LinkedIn: \href{https://www.linkedin.com/in/lucca-cazarine/}{LinkedIn Profile}   
\end{center}

% Section: Introduction
\section*{Introduction}
Aspiring programmer with experience in the field of software development since 2021. Over these years, I have worked on various personal and academic projects, ranging from computer graphics to simple servers, which have provided me with a deeper understanding of programming logic. I am dedicated to improving my skills and technical knowledge, consistently contributing to the growth of the company. I have a keen interest in tackling challenging and innovative projects where I can apply my programming and data analysis skills to solve problems and create effective solutions. I am always eager to take on new challenges and I am open to learning and adapting to emerging technologies and methodologies. With a background in computer science and experience in programming and data analysis projects, I am confident in my ability to meet the company's demands and contribute to its growth. I am organized, committed to meeting deadlines, and constantly strive to enhance my technical and interpersonal skills. I am excited about being part of a dynamic and collaborative team, and I am willing to put in the effort to achieve our common goals.

% Section: Education
\section*{Education}
\begin{itemize}[leftmargin=*]
    \item \textbf{Colégio São Marcos} \hfill Mogi das Cruzes, SP \\
    High School \hfill Period: 2006-2020
    \item \textbf{Pontifícia Universidade Católica of São Paulo - (PUC-SP)} \hfill São Paulo, SP \\
    Bachelor of Computer Science \hfill Expected Graduation: 11/2024
\end{itemize}

% Section: Professional Experience
\section*{Professional Experience}
\begin{itemize}[leftmargin=*]
    \item \textbf{Stefanini Rafael} \hfill São Paulo, SP \\
    Cybersecurity intern \hfill Period: 11/2022 - 05/2023 \\
     Responsibilities:
    \begin{itemize}
        \item Assisted in conducting penetration testing services.
        \item Participated in the pre-sales team for security services.
        \item Updated the SalesForce database.
    \end{itemize}    
\end{itemize}

% Section: Technical Skills
\section*{Technical Skills}
\begin{itemize}[leftmargin=*]
    \item Programming Languages: Python, Java, C++, C, GoLang
    \item Web Development: HTML, CSS, JavaScript
    \item Databases: MySQL, PostgreSQL
    \item Version Control Systems: Git, SVN
    \item LaTex
    \item SalesForce
    \item Microsoft Excel
    \item Neovim    
\end{itemize}

% Section: Projects
\section*{Projects}
\begin{itemize}[leftmargin=*]
    \item \textbf{Simple Server} (GoLang / HTML) \\
    Developed a simple server using the Go programming language and HTML. The server was designed to handle HTTP requests and serve static HTML pages. Implemented routing logic to handle different endpoints and respond with the appropriate HTML content. Also, incorporated basic CSS styling to enhance the visual presentation of the served pages.
    
    \item \textbf{Student Registration and Maintenance System} (Java) \\
    Developed a student registration and maintenance system using Java. The system allows for the management of student information, including names, grades, and registration numbers (RA). Implemented functionalities such as adding new students, updating existing student records, and generating reports. Utilized Java's object-oriented programming principles to design and structure the system effectively. 
    
    \item \textbf{Domino Game} (C) \\
    Developed a domino game using the C programming language. Implemented the rules and mechanics of the game, including shuffling and dealing the domino tiles, allowing players to make valid moves, and determining the winner. 
    
    \item \textbf{Computer Graphics Project} (Java) \\
    Developed a computer graphics project in Java, simulating Microsoft Paint without using pre-built libraries. Implemented various mathematical algorithms to handle shape rendering, color manipulation, and user interactions. Developed functionalities such as drawing lines, shapes, and freehand sketches, selecting colors, and applying transformations. Leveraged mathematical concepts such as matrix operations and geometric calculations to achieve accurate rendering and user-friendly interaction.
    
    \item \textbf{Landing Page} (HTML / CSS) \\
    Developed a landing page project for an infoproducts website. Utilized my front-end knowledge to create an attractive and informative cover. Designed the layout and structure of the page using HTML and applied custom styles using CSS.
    
    \item \textbf{My CV} (LaTex) \\
    Created my own curriculum vitae using LaTeX, a typesetting system. Designed and structured the entire resume, including sections, formatting, and styling, using LaTeX's powerful document preparation capabilities. Leveraged LaTeX's features for precise typography and professional-looking layouts. Implemented various elements such as sections, bullet points, and headers to organize and highlight my qualifications, experience, and skills. Utilized LaTeX's flexibility to easily update and modify the CV as needed.    

\end{itemize}

\section*{Certifications}
\begin{itemize}[leftmargin=*]
\item \textbf{Algorithms Java} – 2021 – Log2Base2
\item \textbf{C Programming} – 2021 – Log2Base2
\item \textbf{Data Structures Java} – 2022 – Log2Base2
\item \textbf{Dynamic Programming} – 2022 – Log2Base2
\item \textbf{Binary Search for Coding Interviews} – 2022 – Log2Base2
\item \textbf{Black Belt Partner Academy Security powerd by Fire Jumper-Presales (Partner Only)} – 2023 – Cisco Black Belt Partner Academy
\end{itemize}

% Section: Languages
\section*{Languages}
\begin{itemize}[leftmargin=*]
    \item Portuguese: Fluent
    \item English: Advanced
    \item Spanish: Basic    
\end{itemize}

\end{document}
